Examining the Multifaceted Impact of Family Size on Happiness, Health, Gender Dynamics, and Financial Well-being

### 2023-04-07 outputs/paper/paper.qmd
Add files via upload

In this context, the objective of this study is to explore the complex interplay between family size and various aspects of family life. The study employs cross-sectional cumulative micro data from the United States spanning from 1972 to 2012. The paper aims to fill a gap in the existing literature by providing a comprehensive analysis of the relationship between the number of children in a family (0, 1, 2, 3, 4) and different variables such as happiness, health, sex distribution, and financial satisfaction, using multiple data sources. Previous research on this topic has often focused on specific aspects of family life or specific sub populations, leaving a gap in the understanding of the broader relationships between family size and different variables.

@@

In [@fig-three], which to provide a more detailed and comprehensive view of the data, the chart displays an analysis and visualization of the number of children had each year from 1972 to 2012, in relation to the level of happiness. In regards to the variable "not too happy," the proportion of individuals who reported feeling unhappy was relatively high in 1974, 1985, 1993, 2004, 2006, and 2008. On the other hand, in regards to the variable "happy," the percentage of individuals reporting feeling happy was relatively high in 1973, 1977, 1994, 2006, and 2012.From the overall data, it can be seen that when people have 1 or 2 children, the most common self-rated health statuses are excellent, fair, and good.

```{r fig.width= 9,fig.height= 6}
#| label: fig-three
#| fig-cap: Relationship between Number of Babies and Happiness by Year
#| echo: false
#| warning: false

>>>>

In this context, the objective of this study is to explore the complex interplay between family size and various aspects of family life. This paper analyzes the results of the General Social Survey, which was conducted between 1972 and 2012 to explore various aspects of society during that time frame.The paper aims to fill a gap in the existing literature by providing a comprehensive analysis of the relationship between the number of children in a family (0, 1, 2, 3, 4) and different variables such as happiness, health, sex distribution, and financial satisfaction, using multiple data sources. Previous research on this topic has often focused on specific aspects of family life or specific sub populations, leaving a gap in the understanding of the broader relationships between family size and different variables.

@@

In [@fig-three], which to provide a more detailed and comprehensive view of the data, the chart displays an analysis and visualization of the number of children had each year from 1972 to 2012, in relation to the level of happiness. In regards to the variable "not too happy," the proportion of individuals who reported feeling unhappy was relatively high in 1974, 1985, 1993, 2004, 2006, and 2008. On the other hand, in regards to the variable "happy," the percentage of individuals reporting feeling happy was relatively high in 1973, 1977, 1994, 2006, and 2012. From the overall data, it can be seen that when people have 1 or 2 children, the most common self-rated health statuses are excellent, fair, and good. Generally speaking, although with the passage of time, the overall proportion of participation in families with one child is large, but it cannot be said that the number of children will affect the level of health scores.

```{r fig.width= 9,fig.height= 6}
#| label: fig-three
#| fig-cap: Percentage between Number of Babies and Happiness by Year
#| echo: false
#| warning: false

ggplot(data[data$happy == "very happy", ], aes(x = year, fill = factor(babies))) +
  geom_bar(position = "fill") +
  facet_wrap(~health, ncol = 5, scales = "free_y") +
  labs(x = "Year", y = "Percentage of Babies", fill = "Number of Babies") +
  theme_bw() +
  scale_y_continuous(labels = scales::percent_format(), expand = c(0.05, 0)) +
  theme(panel.grid.major.x = element_line(color = "grey", size = 0.1),
        strip.text = element_text(size = 10),
        panel.spacing = unit(0.2, "lines"))
